API design for machine learning software: experiences from the scikit-learn project

### 2013-06-28 paper.tex
the scikit-learn -> scikit-learn

Finally, predictors should also provide a \texttt{score} function to assess the
performance on some input data. In supervised learning estimators, this method
takes as input arrays \texttt{X\_test} and \texttt{y\_test} and typically
computes the coefficient of determination between \texttt{y\_test} and
\texttt{predict(X\_test)} in regression, or the accuracy
in classification.
The only requirement is that the \texttt{score} method return a value
that quantifies the quality of its predictions (the higher, the better).
Unsupervised learning estimators may also expose a \texttt{score} function
to compute, for instance, the likelihood of the given data under its model.

@@

Optionally, the model selection algorithms
also take a cross-validation scheme and a score function.  \sklearn provides
various such cross-validation schemes, including $k$-fold (default),
stratified $k$-fold and leave-one-out.
The score function used by default is the estimator's \texttt{score} method,
but the library provides a variety of
alternatives that the user can choose from,
including accuracy, AUC and $F_1$ score for classification,
coefficient of determination and mean squared error for regression.

@@

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to a radial basis function kernel \texttt{"rbf"}.
An SVM with a linear kernel accepts a \texttt{gamma} parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, just like any other classifier:
it delegates the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).

>>>>

Finally, predictors should also provide a \texttt{score} function to assess the
performance on some input data. In supervised learning estimators, this method
takes as input arrays \texttt{X\_test} and \texttt{y\_test} and typically
computes the coefficient of determination between \texttt{y\_test} and
\texttt{predict(X\_test)} in regression, or the accuracy
in classification.
The only requirement is that the \texttt{score} method return a value
that quantifies the quality of its predictions (the higher, the better).
Unsupervised learning estimators may also exposes a \texttt{score} function
to compute, for instance, the likelihood of the given data under its model.

@@

Optionally, the model selection algorithms
also take a cross-validation scheme and a score function.  \sklearn provides
various such cross-validation schemes, including $k$-fold (default),
stratified $k$-fold and leave-one-out.
The score function used by default is the estimator's \texttt{score} method,
but the library provides a variety of
alternatives that the user can choose from,
including accuracy, AUC and $F_1$ score for classification,
$R^2$ score and mean squared error for regression.

@@

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to \texttt{"rbf"}.
An SVM with a linear kernel accepts a $\gamma$ parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, just like any other classifier:
it delegates the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).
